Community-Conditioned Language Models

### 2020-11-12 paper/paper.tex
second attempt

The \emph{speech community} is an important concept 
in the study of linguistic variation.
Any social group exhibiting some degree of linguistic idiosyncrasy
may be considered a speech community \citep{Gumperz1972}.
Linguistic communication requires that participants share 
\emph{common ground} \citep{Stalnaker2002} knowledge of certain norms, 
including the meaning of words, syntactic structure, and patterns of interaction.
Speakers often assume that these norms are common ground based on joint membership
in some community \cite{Clark1996}.

@@

Broadly construed, we want to investigate two questions.  First, we
are interested in the variation of to what extent are various
communities exhibiting various level of linguistic complexity.

>>>>

Linguistic communication requires that speakers share 
knowledge of certain linguistic conventions, such as syntactic structure, 
word meaings, and accepted patterns of interaction.
Speakers assume that these conventions are common ground based on joint membership
in some community \cite{Clark1996}.
Such a community may range in size and specificity from the very large and general
such as \emph{speakers of a language} to very small and specific, such as 
of a dialectical region

\emph{common ground} \citep{Stalnaker2002}

@@

The \emph{speech community} is an important concept 
in the study of linguistic variation.
Any social group exhibiting some degree of linguistic idiosyncrasy
may be considered a speech community \citep{Gumperz1972}.

Broadly construed, we want to investigate two questions.  First, we
are interested in variation in the level of linguistic complexity
exhibited by different communities.
